---
title: "Screening for a Separate Fast-Guess Population"
date: "July 2026"
output: 
  html_document:
    code_folding: hide
    toc: TRUE
    toc_depth: 2
    toc_float: true
---

# Studies 1 and 2 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(dplyr)
library(diptest)
library(patchwork)
library(knitr)
library(readxl)
library(purrr)
library(ggplot2)
library(scales)
library(BayesFactor)
library(effectsize)

library(extrafont)
extrafont::loadfonts(device = "all")
windowsFonts(mono  = "DejaVu Sans", sans = "DejaVu Sans")
#windowsFonts()
```

```{r load}
mardown_path = rstudioapi::getActiveDocumentContext()$path
root_path = sub("(.*time_to_jump).*", "\\1", mardown_path)

data_path = paste0(root_path, "/3_simulators/data/ttj_raw_data.csv")
df_all = read.csv(data_path) 
df_all = df_all[-which(is.na(df_all$rt)), ] #delete timeouts
df_study1 = df_all %>%
  dplyr::filter(trial_class == "critical") %>%
  dplyr::mutate(
    participant = as.integer(pp_nr),
    correct = as.integer(correct),
    symbol = symbol_type,
    RT = rt/1000,
    rt_ms = rt
  ) %>%
  select(participant, condition, symbol,
         RT, rt_ms, correct)
df_study1$study = 1
df_study1$study_label = "Study 1"
df_study1$procedural_cutoff_ms = 500
df_study1$symbol = car::recode(df_study1$symbol, "'letter'=0; 'number'=1")

data_path = paste0(root_path, "/3_simulators/data/ttj_s2_raw_data.csv")
df_all = read.csv(data_path) 
df_all = df_all[-which(is.na(df_all$rt)), ] #delete timeouts
df_study2 = df_all %>%
  dplyr::filter(trial_class == "test") %>%
  dplyr::mutate(
    participant = as.integer(pp_nr),
    correct = as.integer(correct),
    symbol = brightness,
    RT = rt,
    rt_ms = rt * 1000
  ) %>%
  select(participant, condition, symbol,
         RT, rt_ms, correct)
df_study2$study = 2
df_study2$study_label = "Study 2"
df_study2$procedural_cutoff_ms = 900
df_study2$symbol = car::recode(df_study2$symbol, "'dark'=0; 'bright'=1")


df_all_studies = rbind(df_study1, df_study2)
```

```{r sanity}
calc_sanity = function(df) {
  df %>%
    dplyr::group_by(study_label, condition) %>%
    dplyr::summarise(
      n_subj = n_distinct(participant),
      n_trials = n(),
      mean_acc = mean(correct),
      median_rt = median(rt_ms),
      .groups = "drop"
    )
}

sanity_results = calc_sanity(df_all_studies)
sanity_results %>% 
  dplyr::mutate(mean_acc = round(mean_acc, 2), median_rt = round(median_rt, 0)) 
```

```{r helpers}
my_cutoff_ms = 300
my_caf_binwidth = 25

no_leading_zero = function(x) {
  out = scales::number(x, accuracy = 0.01, trim = TRUE)
  out = sub("^0\\.", ".", out)
  out = ifelse(x %% 1 == 0, as.character(as.integer(x)), out)
  out
}

bf_one_sample = function(x, mu = 0.5, bf = "01") {
  if (length(na.omit(x)) < 2) return(NA_real_)
  bf10 = BayesFactor::extractBF(BayesFactor::ttestBF(x = x, mu = mu), onlybf = TRUE)
  if (bf == "01") 1 / bf10 else bf10
}

calc_caf = function(df, binwidth = my_caf_binwidth, min_n = 20) {
  upper = ceiling(max(df$rt_ms, na.rm = TRUE) / binwidth) * binwidth
  breaks = seq(0, upper, by = binwidth)
  df %>% 
    dplyr::mutate(rt_bin = cut(rt_ms, breaks = breaks)) %>%
    dplyr::group_by(study_label, procedural_cutoff_ms, condition, rt_bin) %>%
    dplyr::summarise(
      mean_rt = mean(rt_ms, na.rm = TRUE),
      n_correct = sum(correct, na.rm = TRUE),
      n = dplyr::n(),
      acc = mean(correct, na.rm = TRUE),
      .groups = "drop") %>%
    dplyr::filter(n >= min_n) %>%
    dplyr::rowwise() %>%
    dplyr::mutate(
      ci_low = binom.test(n_correct, n)$conf.int[1],
      ci_high = binom.test(n_correct, n)$conf.int[2],
      above_chance = ci_low > 0.5
    ) %>%
    dplyr::ungroup()
}

calc_caf_threshold = function(caf_df) {
  caf_df %>%
    dplyr::group_by(study_label, condition) %>%
    dplyr::filter(above_chance) %>%
    dplyr::slice_min(mean_rt, n = 1, with_ties = FALSE) %>%
    dplyr::ungroup() %>%
    dplyr::select(study_label, condition, mean_rt, n, acc, ci_low, ci_high)
}

plot_distributions = function(df, plot_title, 
                              condition_levels, condition_labels, condition_cols, 
                              xlim_up, binwidth, alpha_value = 0.6) {
  cutoff_df = df %>%
    dplyr::distinct(procedural_cutoff_ms)
  
  df %>%
    dplyr::mutate(
      condition = factor(condition, levels = condition_levels, ordered = TRUE),
      resp = factor(ifelse(correct == 1, "correct", "incorrect"), levels = c("correct", "incorrect"))) %>%
    ggplot(aes(x = rt_ms, color = condition, linetype = resp, group = interaction(condition, resp))) +
    geom_freqpoly(binwidth = binwidth, linewidth = 0.8, alpha = alpha_value) +
    geom_vline(data = cutoff_df, aes(xintercept = procedural_cutoff_ms), inherit.aes = FALSE,
               linetype = "dashed", color = "black") +
    coord_cartesian(xlim = c(0, xlim_up)) +
    scale_color_manual(name = "Condition", values = setNames(condition_cols, condition_levels), 
                       breaks = condition_levels, labels = condition_labels) +
    scale_linetype_manual(name = "Response", values = c("correct" = "solid", "incorrect" = "dashed"), 
                          labels = c("correct" = "Correct", "incorrect" = "Incorrect")) +
    guides(color = guide_legend(order = 1, title.position = "top", title.hjust = 0.5, ncol = 1, 
                                override.aes = list(linetype = "solid")),
           linetype = guide_legend(order = 2, title.position = "top", title.hjust = 0.5, ncol = 1, 
                                   override.aes = list(color = "black"))) +
    labs(title = plot_title, x = "Response Time (ms)", y = "Count") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.line = element_line(color = "black"),
          legend.position = c(0.98, 0.98),
          legend.justification = c("right", "top"),
          legend.box = "vertical",
          legend.direction = "vertical",
          legend.background = element_rect(fill = "white", color = "lightgrey", linewidth = 0.4),
          legend.box.background = element_blank(),
          legend.margin = margin(4, 6, 4, 6),
          legend.box.margin = margin(0, 0, 0, 0))
}
```

## RT distributions

```{r distributions}
p_dist_1 = plot_distributions(
  df_study1,
  plot_title = "Study 1",
  condition_levels = c("acc", "implicitDeadline", "explicitDeadline"),
  condition_labels = c("Accuracy", "Implicit Deadline", "Explicit Deadline"),
  condition_cols = c("#6B6B6B", "#6A33A2", "#008080"),
  xlim_up = 900,
  binwidth = 10,
  alpha_value = 0.6
)

p_dist_2 = plot_distributions(
  df_study2,
  plot_title = "Study 2",
  condition_levels = c("control", "explicitDeadline"),
  condition_labels = c("Control", "Explicit Deadline"),
  condition_cols = c("#6B6B6B", "#008080"),
  xlim_up = 1500,
  binwidth = 20,
  alpha_value = 0.6
)

p_dist_1 
p_dist_2
```

## Conditional accuracy functions

```{r caf_compute}
caf_results_1 = df_all_studies %>%
  dplyr::filter(study_label == "Study 1") %>%
  calc_caf(binwidth = my_caf_binwidth, min_n = 20)

caf_results_2 = df_all_studies %>%
  dplyr::filter(study_label == "Study 2") %>%
  calc_caf(binwidth = my_caf_binwidth, min_n = 20)
```

```{r caf_plot}
plot_caf = function(caf_df, 
                    condition_levels, condition_labels, condition_cols,
                    my_linewidth = 0.6,
                    xlim_up = 1150,
                    base_font_size = 9,   
                    title_font_size = 11,  
                    key_height = 0.8,   
                    title_gap = -3) {   

  cutoff_df = caf_df %>%
    dplyr::distinct(procedural_cutoff_ms)

  caf_df %>%
    dplyr::mutate(
      condition = factor(
        condition, 
        levels = condition_levels, 
        labels = condition_labels,
        ordered = TRUE
      )
    ) %>%
    ggplot2::ggplot(
      ggplot2::aes(
        x = mean_rt,
        y = acc,
        color = condition,
        fill = condition,
        linetype = condition,
        shape = condition
      )
    ) +
    ggplot2::geom_ribbon(
      ggplot2::aes(ymin = ci_low, ymax = ci_high),
      alpha = 0.15,
      color = NA
    ) +
    ggplot2::geom_point(size = 1.5) +
    ggplot2::geom_line(linewidth = my_linewidth, alpha = 1) +
    ggplot2::geom_hline(
      yintercept = 0.5,
      linetype = "longdash",
      color = "black",
      linewidth = 0.4
    ) +
    ggplot2::geom_vline(
      data = cutoff_df,
      ggplot2::aes(xintercept = procedural_cutoff_ms),
      inherit.aes = FALSE,
      linetype = "dotted",
      color = "black",
      linewidth = 0.4
    ) +
    ggplot2::coord_cartesian(xlim = c(0, xlim_up), ylim = c(0, 1)) +
    ggplot2::scale_y_continuous(labels = no_leading_zero) +
    ggplot2::scale_color_manual(
      values = stats::setNames(condition_cols, condition_labels),
      breaks = condition_labels
    ) +
    ggplot2::scale_fill_manual(
      values = stats::setNames(condition_cols, condition_labels),
      breaks = condition_labels
    ) +
    ggplot2::scale_linetype_manual(
      values = stats::setNames(rep("solid", length(condition_labels)), condition_labels),
      breaks = condition_labels
    ) +
    ggplot2::scale_shape_manual(
      values = stats::setNames(rep(16, length(condition_labels)), condition_labels),
      breaks = condition_labels
    ) +
    ggplot2::labs(
      title = unique(caf_df$study_label),
      x = "Response Time Bin (ms)",
      y = "Proportion Correct",
      color = "Condition",
      fill = "Condition",
      linetype = "Condition",
      shape = "Condition"
    ) +
    ggplot2::guides(
      color = ggplot2::guide_legend(
        order = 1, title.position = "top", title.hjust = 0.5, ncol = 1,
        override.aes = list(alpha = 1, linewidth = my_linewidth, size = 1.5)
      ),
      fill = "none", linetype = "none", shape = "none"
    ) +
    ggplot2::theme_minimal(
      base_family = "DejaVu Sans",
      base_size   = base_font_size
    ) +
    ggplot2::theme(
      text = ggplot2::element_text(size = base_font_size),
      plot.title = ggplot2::element_text(hjust = 0.5, size = title_font_size),
      axis.title = ggplot2::element_text(size = base_font_size),
      axis.text  = ggplot2::element_text(size = base_font_size, color = "black"
      ),
      panel.grid.major.y = ggplot2::element_blank(),
      panel.grid.minor.y = ggplot2::element_blank(),
      panel.grid.major.x = ggplot2::element_blank(),
      panel.grid.minor.x = ggplot2::element_blank(),
      axis.line  = ggplot2::element_line(color = "black", linewidth = 0.4),
      axis.ticks = ggplot2::element_line(color = "black", linewidth = 0.4),
      legend.position      = c(0.98, 0.1),
      legend.justification = c("right", "bottom"),
      legend.direction     = "vertical",
      legend.box           = "vertical",
      legend.key.height = grid::unit(key_height, "lines"),
      legend.key.width  = grid::unit(1.4, "lines"),
      legend.title = ggplot2::element_text(
        size   = base_font_size, hjust  = 0.5,
        margin = ggplot2::margin(b = title_gap)       
      ),
      legend.text = ggplot2::element_text(size = base_font_size),
      legend.background = ggplot2::element_rect(fill = "white", color = "lightgrey", linewidth = 0.4),
      legend.box.background = ggplot2::element_blank(),
      legend.margin = ggplot2::margin(4, 6, 4, 6),
      legend.box.margin = ggplot2::margin(0, 0, 0, 0)
    )
}

p_caf_1 = plot_caf(
  caf_results_1,
  condition_levels = c("acc", "implicitDeadline", "explicitDeadline"),
  condition_labels = c("Accuracy", "Implicit Deadline", "Explicit Deadline"),
  condition_cols   = c("#6B6B6B", "#6A33A2", "#008080"),
  xlim_up = 1000
)

p_caf_2 = plot_caf(
  caf_results_2,
  condition_levels = c("control", "explicitDeadline"),
  condition_labels = c("Control", "Explicit Deadline"),
  condition_cols   = c("#6B6B6B", "#008080"),
  xlim_up = 1000
)

fig_d1 = p_caf_1 + p_caf_2 +
  patchwork::plot_layout(guides = "keep") &
  ggplot2::theme(
    plot.margin = ggplot2::margin(t = 10, r = 5, b = 5, l = 5)
  )

fig_d1

ggplot2::ggsave(plot = fig_d1,
  filename = "Figure_D1_screening.png",
  device = ragg::agg_png,
  path = paste0(root_path, "/4_R_script/"),
  width = 16, height = 9, units = "cm", dpi = 300
)
```

## Empirical boundaries

```{r caf_thresholds}
caf_results = dplyr::bind_rows(caf_results_1, caf_results_2)

calc_caf_threshold(caf_results) %>%
  dplyr::mutate(
    mean_rt = round(mean_rt, 0),
    acc = round(acc, 2),
    ci_low  = round(ci_low, 2),
    ci_high = round(ci_high, 2)
  )

rt_thresholds_study = calc_caf_threshold(caf_results) %>%
  dplyr::select(study_label, condition, rt_cutoff = mean_rt)

empirical_thresholds = rt_thresholds_study %>%
  dplyr::transmute(study_label, condition,
                   empirical_threshold_ms = rt_cutoff)
```

## Fast-response prevalence 

```{r fixed_prevalence}
df_all_studies %>%
  dplyr::group_by(study_label, condition) %>%
  dplyr::summarise(
    n_total       = dplyr::n(),
    n_below_300   = sum(rt_ms < 300),
    pct_below_300 = round(mean(rt_ms < 300) * 100, 2),
    acc_below_300 = round(mean(correct[rt_ms < 300], na.rm = TRUE), 3),
    .groups = "drop"
  )
```

```{r empirical_prevalence}
calc_trial_proportions = function(df, thresholds) {
  df %>%
    dplyr::left_join(thresholds, by = c("study_label", "condition")) %>%
    dplyr::group_by(study_label, condition) %>%
    dplyr::summarise(
      n_total = dplyr::n(),
      n_below_empirical = sum(rt_ms < unique(empirical_threshold_ms)),
      pct_below_empirical = mean(rt_ms < unique(empirical_threshold_ms)) * 100,
      .groups = "drop"
    )
}

trial_proportions = calc_trial_proportions(df_all_studies, empirical_thresholds)
trial_proportions %>%
  dplyr::mutate(across(tidyselect::starts_with("pct_"), ~ round(.x, 2)))
```

## Accuracy below the empirical boundary 

```{r empirical_accuracy}
fastregion_acc = df_all_studies %>%
  dplyr::left_join(empirical_thresholds, by = c("study_label", "condition")) %>%
  dplyr::filter(rt_ms < empirical_threshold_ms) %>%
  dplyr::group_by(study_label, condition) %>%
  dplyr::summarise(
    n_below = dplyr::n(),
    n_correct = sum(correct),
    acc_below = mean(correct),
    .groups = "drop"
  ) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(
    ci_low = binom.test(n_correct, n_below)$conf.int[1],
    ci_high = binom.test(n_correct, n_below)$conf.int[2]
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(across(c(acc_below, ci_low, ci_high), ~ round(.x, 3)))
fastregion_acc

df_all_studies %>%
  dplyr::left_join(empirical_thresholds, by = c("study_label", "condition")) %>%
  dplyr::filter(rt_ms < empirical_threshold_ms) %>%
  dplyr::group_by(study_label, participant, condition) %>%
  dplyr::summarise(acc = mean(correct, na.rm = TRUE),
                   n = dplyr::n(), .groups = "drop") %>%
  dplyr::filter(n >= 10) %>%
  dplyr::group_by(study_label, condition) %>%
  dplyr::summarise(
    n_subj = dplyr::n(),
    mean_acc = round(mean(acc), 3),
    ci_low = round(mean(acc) - 1.96 * sd(acc) / sqrt(dplyr::n()), 3),
    ci_high  = round(mean(acc) + 1.96 * sd(acc) / sqrt(dplyr::n()), 3),
    .groups = "drop"
  )
```

## Accuracy below the fixed 300-ms cutoff 

```{r fixed_cutoff_test}
df_all_studies %>%
  dplyr::filter(rt_ms < my_cutoff_ms) %>%
  dplyr::group_by(study_label, participant, condition) %>%
  dplyr::summarise(acc = mean(correct, na.rm = TRUE),
                   n = dplyr::n(), .groups = "drop") %>%
  dplyr::filter(n >= 10) %>%
  dplyr::group_by(study_label, condition) %>%
  dplyr::summarise(
    n_subj = dplyr::n(),
    mean_acc = round(mean(acc), 3),
    t = round(t.test(acc, mu = 0.5)$statistic, 3),
    p = round(t.test(acc, mu = 0.5)$p.value, 3),
    cohens_d = round(effectsize::cohens_d(acc, mu = 0.5)$Cohens_d, 3),
    BF01 = round(bf_one_sample(acc, mu = 0.5, bf = "01"), 3),
    BF10 = round(bf_one_sample(acc, mu = 0.5, bf = "10"), 3),
    .groups  = "drop"
  )
```

## Participant spread in the candidate region

```{r participant_spread}
condition_totals = df_all_studies %>%
  dplyr::distinct(study_label, condition, participant) %>%
  dplyr::count(study_label, condition, name = "n_participants_total")

df_all_studies %>%
  dplyr::left_join(empirical_thresholds, by = c("study_label", "condition")) %>%
  dplyr::filter(rt_ms < empirical_threshold_ms) %>%
  dplyr::count(study_label, condition, participant, name = "n_fast") %>%
  dplyr::group_by(study_label, condition) %>%
  dplyr::summarise(
    n_with_fast = dplyr::n(), # participants with >=1 fast trial
    median_per_pp = median(n_fast),
    q25_per_pp = quantile(n_fast, 0.25),
    q75_per_pp = quantile(n_fast, 0.75),
    max_per_pp = max(n_fast),
    .groups = "drop"
  ) %>%
  dplyr::left_join(condition_totals, by = c("study_label", "condition")) %>%
  dplyr::mutate(pct_with_fast = round(100 * n_with_fast / n_participants_total, 1)) %>%
  dplyr::relocate(n_participants_total, .after = n_with_fast)
```

## Bimodality: Hartigan's dip test

```{r dip_test}
calc_dip_results = function(df) {
  df %>%
    dplyr::filter(correct == 1) %>%
    dplyr::group_by(study_label, participant, condition) %>%
    dplyr::summarise(
      dip_p = dip.test(rt_ms)$p.value,
      n_trials = n(),
      .groups = "drop"
    )
}

summarise_dip_by_condition = function(dip_results, min_trials = 10) {
  dip_results %>%
    dplyr::filter(n_trials >= min_trials) %>%
    dplyr::group_by(study_label, condition) %>%
    dplyr::summarise(
      n_subj = n(),
      n_significant = sum(dip_p < .05),
      pct_significant = mean(dip_p < .05) * 100,
      .groups = "drop"
    )
}

summarise_dip_overall = function(dip_results, min_trials = 10) {
  dip_results %>%
    dplyr::filter(n_trials >= min_trials) %>%
    dplyr::group_by(study_label) %>%
    dplyr::summarise(
      n_subj = n(),
      n_significant = sum(dip_p < .05),
      pct_significant = mean(dip_p < .05) * 100,
      .groups = "drop"
    )
}

dip_results = calc_dip_results(df_all_studies)

summarise_dip_by_condition(dip_results) %>%
  dplyr::mutate(pct_significant = round(pct_significant, 2))
summarise_dip_overall(dip_results) %>%
  dplyr::mutate(pct_significant = round(pct_significant, 2))
```

# Cross-validation: Rafiei and Rahnev (2021)

```{r rr_load, message = FALSE, warning = FALSE}
local_rr_data_path = "C:/Users/Administrator/Downloads/data.xlsx"
rr_data_url = "https://osf.io/nzx7a/download"

rr_data_path = if (file.exists(local_rr_data_path)) {
  local_rr_data_path
} else {
  tmp = tempfile(fileext = ".xlsx")
  download.file(rr_data_url, tmp, mode = "wb")
  tmp
}

df_rr = readxl::read_excel(rr_data_path, sheet = 2) %>%
 rename(participant = Subject, correct = Accuracy) %>%
  dplyr::mutate(rt_ms = RT * 1000, condition = factor(SAT, levels = 1:5, labels = c("extremely_fast", "fast", "medium", "slow", "extremely_slow")))
```

## Sanity check

```{r rr_sanity}
df_rr %>%
  dplyr::group_by(condition) %>%
  dplyr::summarise(
    n_subj = n_distinct(participant),
    n_trials = n(),
    mean_acc = round(mean(correct), 3),
    median_rt = round(median(rt_ms), 1)
  ) 
```

## Conditional accuracy functions

```{r rr_caf, fig.width = 7, fig.height = 4.2}
caf_rr = df_rr %>%
  dplyr::mutate(study_label = "Rafiei & Rahnev", procedural_cutoff_ms = NA_real_) %>%
  calc_caf(binwidth = my_caf_binwidth, min_n = 20)

ggplot(caf_rr, aes(x = mean_rt, y = acc, color = condition, fill = condition)) +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = 0.15, color = NA) +
  geom_point(size = 1.5) +
  geom_line(linewidth = 0.7) +
  geom_hline(yintercept = 0.5, linetype = "dashed") +
  geom_vline(xintercept = 300, linetype = "dotted") +
  coord_cartesian(xlim = c(0, 800), ylim = c(0, 1)) +
  labs(
    x = "Response Time Bin (ms)",
    y = "Proportion Correct",
    color = "SAT condition",
    fill = "SAT condition"
  ) +
  theme_minimal() +
  theme(legend.position = "top")
```

## Empirical boundaries

```{r rr_caf_threshold}
caf_rr %>%
  dplyr::group_by(condition) %>%
  dplyr::filter(above_chance) %>%
  dplyr::slice_min(mean_rt, n = 1) %>%
  dplyr::select(condition, mean_rt, n, acc, ci_low, ci_high) %>%
  dplyr::mutate(
    mean_rt = round(mean_rt, 1),
    acc = round(acc, 3),
    ci_low = round(ci_low, 3),
    ci_high = round(ci_high, 3)
  )
```

## Fast-response prevalence 

```{r rr_prevalence}
df_rr %>%
  dplyr::group_by(condition) %>%
  dplyr::summarise(
    n_total = n(),
    n_below_300 = sum(rt_ms < 300),
    pct_below_300 = round(mean(rt_ms < 300) * 100, 2),
    acc_below_300 = round(mean(correct[rt_ms < 300], na.rm = TRUE), 3),
    .groups = "drop"
  ) 

rt_thresholds = caf_rr %>%
  dplyr::group_by(condition) %>%
  dplyr::filter(above_chance) %>%
  dplyr::slice_min(mean_rt, n = 1, with_ties = FALSE) %>%
  dplyr::ungroup() %>%
  dplyr::select(condition, rt_cutoff = mean_rt)

df_rr %>%
  dplyr::left_join(rt_thresholds, by = "condition") %>%
  dplyr::group_by(condition, rt_cutoff) %>%
  dplyr::summarise(
    n_total = n(),
    n_below_cutoff = sum(rt_ms < rt_cutoff, na.rm = TRUE),
    pct_below_cutoff = round(mean(rt_ms < rt_cutoff, na.rm = TRUE) * 100, 2),
    acc_below_cutoff = round(mean(correct[rt_ms < rt_cutoff], na.rm = TRUE), 3),
    .groups = "drop"
  ) %>%
  dplyr::mutate(rt_cutoff = round(rt_cutoff, 1))
```

## Reproduction of Ratcliff and Kang (2021)

```{r rr_rk_reproduction}
rk_base = df_rr %>% dplyr::filter(condition == "extremely_fast")

dplyr::bind_rows(
  rk_base %>% dplyr::mutate(set = "all responses"),
  rk_base %>% dplyr::filter(rt_ms < 300) %>% dplyr::mutate(set = "RT < 300 ms")) %>%
  dplyr::group_by(set, participant) %>%
  dplyr::summarise(acc = mean(correct), .groups = "drop") %>%
  dplyr::group_by(set) %>%
  dplyr::summarise(
    n_subj = dplyr::n(),
    mean_acc = round(mean(acc), 3),
    t = round(t.test(acc, mu = 0.5)$statistic, 3),
    df = t.test(acc, mu = 0.5)$parameter,
    p = round(t.test(acc, mu = 0.5)$p.value, 4),
    cohens_d = round(effectsize::cohens_d(acc, mu = 0.5)$Cohens_d, 3),
    BF01 = round(bf_one_sample(acc, mu = 0.5, bf = "01"), 3),
    BF10 = round(bf_one_sample(acc, mu = 0.5, bf = "10"), 3),
    .groups  = "drop"
  )
```

## Reproduction check

```{r rk_reproduction_check}
rk_repro_check = function(lower_ms, higher_ms) {
  base = df_rr %>% dplyr::filter(condition == "extremely_fast", rt_ms > lower_ms, rt_ms < higher_ms)
  
  subj_acc = function(d) {
    d %>%
      dplyr::group_by(participant) %>%
      dplyr::summarise(acc = mean(correct), .groups = "drop") %>%
      dplyr::pull(acc)
  }
  
  all_acc  = subj_acc(base)
  fast_acc = subj_acc(dplyr::filter(base, rt_ms < 300))
  
  tibble::tibble(
    lower_ms = lower_ms,
    higher_ms = higher_ms,
    set = c("all responses", "RT < 300 ms"),
    n_subj = c(length(all_acc), length(fast_acc)),
    mean_acc = round(c(mean(all_acc), mean(fast_acc)), 3),
    t = round(c(t.test(all_acc,  mu = .5)$statistic,
                t.test(fast_acc, mu = .5)$statistic), 3),
    df = c(t.test(all_acc, mu = .5)$parameter,
           t.test(fast_acc, mu = .5)$parameter),
    p = round(c(t.test(all_acc,  mu = .5)$p.value,
                t.test(fast_acc, mu = .5)$p.value), 4)
  )
}

cutoffs = tidyr::crossing(lower_ms = c(0, 150), higher_ms = c(999999, 1500))

cutoffs %>%
  purrr::pmap_dfr(function(lower_ms, higher_ms) {
    rk_repro_check(lower_ms = lower_ms, higher_ms = higher_ms)
  })
```

## Accuracy below the fixed 300-ms cutoff

```{r rr_fixed_cutoff_test}
df_rr %>%
  dplyr::filter(rt_ms < my_cutoff_ms) %>%
  dplyr::group_by(condition, participant) %>%
  dplyr::summarise(acc = mean(correct, na.rm = TRUE),
                   n = dplyr::n(), .groups = "drop") %>%
  dplyr::filter(n >= 10) %>%
  dplyr::group_by(condition) %>%
  dplyr::summarise(
    n_subj = dplyr::n(),
    mean_acc = round(mean(acc), 3),
    t = ifelse(dplyr::n() >= 2, round(t.test(acc, mu = 0.5)$statistic, 3), NA_real_),
    p = ifelse(dplyr::n() >= 2, round(t.test(acc, mu = 0.5)$p.value, 3), NA_real_),
    cohens_d = ifelse(dplyr::n() >= 2, round(effectsize::cohens_d(acc, mu = 0.5)$Cohens_d, 3), NA_real_),
    BF01 = round(bf_one_sample(acc, mu = 0.5, bf = "01"), 3),
    BF10 = round(bf_one_sample(acc, mu = 0.5, bf = "10"), 3),
    .groups = "drop"
  )
```

## Accuracy below the empirical boundary

```{r rr_empirical_accuracy}
df_rr %>%
  dplyr::left_join(rt_thresholds, by = "condition") %>%
  dplyr::filter(rt_ms < rt_cutoff) %>%
  dplyr::group_by(participant, condition) %>%
  dplyr::summarise(acc = mean(correct, na.rm = TRUE), n = n(), .groups = "drop") %>%
  dplyr::filter(n >= 10) %>%
  dplyr::group_by(condition) %>%
  dplyr::summarise(
    n_subj = n(),
    mean_acc = round(mean(acc, na.rm = TRUE), 3),
    ci_low = round(mean(acc) - 1.96 * sd(acc) / sqrt(n()), 3),
    ci_high = round(mean(acc) + 1.96 * sd(acc) / sqrt(n()), 3),
    .groups = "drop"
  )
```

## Bimodality: Hartigan's dip test

```{r rr_dip}
dip_rr = df_rr %>%
  dplyr::filter(correct == 1) %>%
  dplyr::group_by(participant, condition) %>%
  dplyr::summarise(dip_p = dip.test(rt_ms)$p.value, n_trials = n(), .groups  = "drop")

dip_rr %>%
  dplyr::filter(n_trials >= 10) %>%  
  dplyr::group_by(condition) %>%
  dplyr::summarise(n_subj = n(), n_significant = sum(dip_p < .05), pct_significant = round(mean(dip_p < .05) * 100, 2), .groups = "drop")
```
